Which ``Bad Smells'' can be Ignored?

### 2016-03-11 Manuscript.tex
Updates from ShareLaTeX

\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
\usepackage{times}
\pagenumbering{arabic} 
\begin{document}

@@

\title{  Which ``Bad Smells'' can be Ignored?}
\numberofauthors{2} 
\author{  
\alignauthor
Rahul~Krishna, Tim Menzies  \\
       \affaddr{Computer Science, NC State, USA}\\
       {\{i.m.ralk,~tim.menzies\}@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE, College Park, USA}\\ 
       {llayman@cese.fraunhofer.org}
\setlength{\columnsep}{7mm}}
\maketitle
\begin{abstract} 
The literature lists dozens of bad smells which might
be detrimental to a software system.
But which are relevant to the current project
and which can be ignored?
Developers, text books, and tools
disagree on which bad smells are important. 
Specifically, it is unclear at what threshold values
a measurement should trigger code refactorings  since
most studies do not offer
{\em both} measurable metrics {\em and} a threshold for their proposed bad smells.

This paper proposes   XTREE, a tool to   prioritize  bad  smells.
Given an historical log of defects seen previously in the code, XTREE deprioritizes bad smells that have little or no support in that log.

When XTREE's recommendations are compared to 
  those found by previous work (Shatnawi, Alves, and Borges.)
  If code modules are  changed to avoid the bad
  smells found by XTREE,  that changed system
  has significantly fewer expected defects.
  Also, XTREE   endorses
  changes to far fewer code metrics.
  Hence, it is 
  a better tool for ruling out irrelvant bad smells.
  For example, the XTREE results show that many of the bad smells learned 
  by Shatnawi, Alves, and Borges can be ignored.

Based on these results, we endorse using bad smells to  
guiding refactoring. However, not all bad smells
are   relevant to the current project.
Hence, it is important
to  prioritize the importance of specific bad smells within the context of each project.

@@

\noindent
According to   Fowler~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk of introducing errors}'' (our italics).
\end{quote}
The literature is divided on the merits of bad smells.
Much research  endorses using them as a guide
code change. For example,
the recent literature review of Tufano et al. at ASE'15~\cite{Tufano2015}  
lists dozens of  
papers proposing bad smell detection and repair tools.

On the other hand, other papers cast doubts on the value of use bad smalls
as triggers for code change.
As we show in this paper,  
 tools and text books and developers can disagree on what bad smells
are important enough to hunt down and eliminate. Our findings
are consistent with other research suggesting that bad
smells may not be a useful way to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

Debates on when/what code should be restructed are interesting, especially
in the current context of  widely-used SE practices such as
test-driven agile development~\cite{beck2003test,janzen05,williams2003test,george2003initial}.
In that approach, developers are always asking themselves ``should I refactor this code''?
Bad smells are a widely used  technique for deciding when to refactor\footnote{Evidence: As of  early 2016, ACM Digital Portal reports 
the Fowler text has 6434 references. Also, bad smell-based research
is widely reported. A search  on {\em "bad smell"+programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.}.
Hence it is important to understand the value of
 bad smells.  
Valuable development resources can be wasted if developers
refactor their code based on   bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

To address this problem, we propose the XTREE
tool to judge refactorings
proposed by developers.
  XTREE requires:
     \begin{itemize}
         \item An historical log of defects seen previously in the code;
         \item  Bad smells expressed in terms of the 
          metrics   in that log;
         \item Some proposed refactorings justified using those bad smells.
     \end{itemize}
Given that information,  XTREE can determine which
  proposed refactorings are be ignored
since they are not justifiedable  
with respect to the history of this project.

@@

{\em PROBLEM \#1:} As discussed in the next section, programmer
   cognitive biases result in different
developers declaring that
bad smell X or Y is most important. 
 XTREE offers a way to assess
 competing claims about different refactorings.

{\em PROBLEM \#2:} Not all bad smells can be fixed. 
Consider
a bad smell that is triggering on some very long method,
yet that method must be passed as a single closure
to a third-party GUI toolkit.  This is one
example of a common problem-- when new code must
be combined with code from other developers,
sometimes the constraints imposed by the other code
lead unavoidably to bad smells. In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

To address this second
  problem, we let
XTREE {\em reason optimistically} to find the set
$R_0$ of refactorings that might be useful
(for details on how that optimistic reasoning
is implemented, see \tion{rq}).
Since that set was generated optimistically,
the space of actually usable refactorings is 
the possibly smaller subset $R_1 \subseteq R_0$.
If the developer's proposed refactoring $R_2$ is
not in $R_0$, then it cannot be in the smaller
set $R_1$.  As shown
in this paper's experiments,  XTREE's
recommendations typically include only a small subset of
the code metrics. That is, we
can still rule out some proposed refactorings
since many of those proposals fall outside of the space
of refactorings suggested by XTREE.

{\em PROBLEM \#3:}  
Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
{\em both} a metrics and a threshold for their proposed bad smells. For example,  Darcy and Kemerer~\cite{darcy05}
discuss what OO design metrics might defect bad smells (e.g. a excessive
depth of inheritance tree) but they never comment on what thresholds
means that some section of code starts to smell bad.  
In all our  reading of the recent literature,
the only work we can find from other researchers that
offers metrics {\em and} thresholds come
from Shatnami~\cite{Shatnawi10}
and  Alves et al.~\cite{Alves2010} (for details on those
methods, see \tion{methods}).
One potential problem with their approaches is that 
they do not explore the interconnections between sets
of code metrics. This is important if sets of
code metrics have to be changed at the same time.
For example, it is not possible to refactor a
long method it several smaller ones without increasing
the coupling metrics of a class. 
More generally, we say that   bad smell thresholds should be
{\em conjunctions} of metric+thresholds pairs that need to be changed {\em togehter}.
Yet Shatnami~\cite{Shatnawi10}
and Alves et al.   report   {\em disjunctions} of multiple metric/thresholds~\cite{Shatnawi10,Alves2010}
which could be separately and  inappropriately used
to guide refactoring.

@@

{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite since
code refactorings is meant to
preserve the semantics of the code (i.e. the same tests
should pass before and after the refactoring). 
Also, it many not be practical
 to assessing refactorings by making the
refactorings,  then seeing what happens to that code for the rest
of the project. In a test-driven agile project, as
SCRUM meetings change what stories are implemented next,
the operational profile that lead to defects in the old
code may not be repeated in future executions. 
To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of systems: 
\begin{enumerate}
    \item One system to propose changes;
\item Another, completely separate, system to assess
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}, constructed in 2002.
Our problem with using tools like QMOOD
is that   quality models learned from other projects,
may perform poorly when applied to new projects~\cite{me12d}.

To solve this fourth problem, this study  eschews
older quality models like QMOOD.
Instead, we use
Random Forests~\cite{Breiman2001} to learn defect predictors
that are specific to the systems   studied here.

 As to XTREE's limitations, the tool 
  can only comment
on refactorings expressed in the   terminology
as the data
  in the historical log of a project.
If developers want to justify their refactorings
via bad smells expressed in other terminology,
then a XTREE-style analysis must   wait till 
data about those new
terms has been collected.

Another  aspect to note about XTREE  is that the tool assumes
Fowler's bad smells
should be assessed only via their contribution to software defects
(evidence: see the section in italics of the quote
that starts this introduction). Some researchers 
 comment that   debating bad smells is  useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
debates about refactorings can   (a)~introducing new comers to the code base or (b)~share knowledge around a team
about interactions within the code. In that view, 
the concept of refactoring can be useful
even if it does not address issues of defects. 
That said, using
defect predictors,
it is possible to operationalize XTREE
while it might be harder to otherwise operationalize the assessment of bad smells.
Hence, 
this paper assumes that {\em better} bad smells and
bettering at finding code changes that  {\em reducing} the chances
that the new code will contain defects.

The rest of this paper is structured as follows. XXX.
discusses the cognitive
biases which make developers disagree on the relevance of those bad smells to
their particular projects.  
 That discussion is our motivation for developing the XTREE  tool
that   carefully assesses the merit of old bad smells to new projects.  XTREE is presented in Section 3 and evalauted in the rest of the paper.

@@

\newpage
\subsection{Assessment Oracles}
\label{sect:eval}
Prior work~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} 
used the QMOOD hierarchical quality model ~\cite{Bansiya02} to assess the results of their refactorings
Since the QMOOD method is quite old (2002), we  used Random Forests~\cite{Breiman2001} to build
the assessment methods.

@@

The Scott-Knott  results are presented in the form of line diagrams like those shown on the right-hand-side of the following example table.
The black dot shows the median \eq{diff} values and the horizontal likes stretch 
from the 25th percentile to the 75th percentile (a region called the inter-quartile
range, or IQR).
\begin{center}
{\small
  Example 
\begin{tabular}{{l@{~~~}l@{~~~}r@{~~~~}r@{~~~}c@{}r}} 
\arrayrulecolor{lightgray}
\rowcolor{lightgray}\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
1 &      XTREE &    62  &  6 & \quart{67.2}{7}{69.6}{115}  \\
\hline 2   & Alves        &    40  & 20  & \quart{45}{10}{50}{10}\\
\hline 3 &      CD &    24  &  18 & \quart{28}{14.4}{35.2}{115} \\
\hline 4   & Shatnawi        &    15  & 10  & \quart{28}{5}{30}{10}\\\hline
\end{tabular}}
\end{center}
In this example table, the rows are  sorted on the median values of each method. Note that all the methods have \eq{diff} $\gt 0\%$; i.e. all these methods reduced the expected value of the performance score in that experiment while XTREE achieved the greatest reduction (of 62\% from the original value).
The above example table has a  left-hand-side  {\bf Rank} column, computed using the
Scott-Knott test described above. In this example table, XTREE is ranked the best, while Shatnami is  ranked   worst.

@@

\fig{jur} shows the comparison results.  The Alves and Shatnami
entries show net effects of applying (seperately) all the disjuncts
proposed by those methods.

Three data sets are very responsive to defect reduction suggestions:
Jedit, Ant, and Ivy (all of which show best case improvements over 50\%.
 The Jedit results are  
surprisingly uniform  suggesting that in that data set that
our methods all find the same ways to reduce the expected number of
defects.

@@

\subsection{RQ2}
\input{tex/rq2.tex}

\subsection{RQ3}
\begin{figure*} 
\centering
\includegraphics[width=\linewidth]{figs/changes0.png}
\caption{XTREE results.
While \fig{counts} are the {\em number} of times a code metric was changed,
\fig{changes} shows {\em how far} each code metric was changed. Each vertical bar
marks the 27,50,75th percentile change seen in 40 repeats. }
\label{figs:changes}
\end{figure*}

@@

XXXX only reorg due to the issues in the data sets.
we are stuck with that. note hwever that if
projects improved their data collection then
our techniques woudl still apply, unmodifed, to the revised data sets. so here we are ding what we can with the data currently available (and also ensuring we are good to go on future data)

@@

@@

\subsection{ Learner Bias}
For building the defect predictors in this study, we elected
to use  Random Forests. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}. Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.

That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions. The above code used a set of variables which future
work should vary in order to test the internal validity of our conclusions:

\bi
\item The clustering scheme, WHERE, divides data into groups of size $\alpha=\sqrt{N}$;
\item XTREE considered a sibling useful if it's score was less than $\gamma=0.5$ times the mean score of the current leaf.
 \ei

\subsection{  Sampling bias} 
Sampling bias threatens any data mining experiment; i.e., what matters
there may not be true here. For example, the data sets used here comes from two sources
(Seigmund et al. and Jureczko et al.) and any biases in their selection procedures
threaten the validity of these results. 
That said,
the best we can do is define our methods and publicize our data and code so that other researchers can
try to repeat our results and, perhaps, point out a previously unknown bias
in our analysis. Hopefully, other researchers will emulate our methods in
order to repeat, refute, or improve our results.

\subsection{  Evaluation Bias}\label{sect:coc}
Another threat to validity of this work is our use
of predictors learned on the training data to assess the impact of our planners.
This issue was discussed in detail in \tion{trust}.

To those notes, we add a few more details. If possible, planners should be assessed via some external oracle that can accurately assess new examples. For example, in search-based software engineering,
examples can be assigned objective scores via  some model. In this approach, a changed example can be assessed by
generating actual objective scores from the model.

@@

The POM3 model~\cite{boehm2003using},~\cite{port2008} is a tool for exploring management challenges. POM3 implements the Boehm and Turner model of agile programming~\cite{boehm2003balancing} where teams select tasks as they appear in the scrum backlog.  POM3 can study the implications of different ways to adjust task lists in the face of shifting priorities. The model outputs estimated task completion rates; programmer idle rates; and total overall cost. POM3 models requirements as a dependency tree. A single requirement in the tree of a prioritization value has a cost, along with a list of child-requirements and dependencies. Before any requirement can be satisfied, its children and dependencies must first be satisfied. POM3 simulates changing priorities by making teams aware of random items in the requirements tree at random intervals, thus forcing teams to constantly readjust their "to do" lists. For further details on this model see~\cite{boehm2003using},~\cite{port2008}, and~\cite{boehm2003balancing}.

\fig{coc} shows results from using POM3 as an oracle to assess our planning methods and their ability to reduce the project cost. In this experiment, we generated a training and testing set with 1000 randomly generated instances, which we passed to our four methods.
40 times, we let those methods propose changes to those projects. 
For assessment purposes, the changed projects were then fed back to the POM3
oracle.

Using this approach, it is possible to assess the value of a plan by measuring its
effectiveness with respect to some ground truth (in this case, the POM3 model).
As shown in \fig{coc}, XTREE reduces the cost by 59\% thereby passing this assessment. These results from the POM3 model further endorse our previous conclusions; i.e. compared to three other methods,  XTREE's supervised methods are best for generating plans on how to change example projects.

\section{Conclusions}

The planner proposed in this paper proposes changes to software project details in order to improve the expected
value of the performance scores of that part of the project.
To evaluate these planners,
data miners can be used to build oracles to assess planners.
Such planners should be {\em trust-increasing}; i.e. they should propose changes that generate
changed examples that are closer to the training data of the data miner.
One caveat here is that the evaluations we can make on the planner are only as good as the predictive
performance of the data miner. Hence, if domain data does not support satisfactory predictors, then
planning in that domain cannot be evaluated.

Four planners were assessed here for the tasks of reducing defects and runtimes. 
Three of the methods come from our prior publications~\cite{me12c,krishna15}, and the conclusion of this
paper is that a novel fourth method clearly out-performs the other three
(measured in terms of {\em effectiveness, succinctness, and surprise}).
We conjecture that XTREE worked better than the rest since:
\bi
\item
It uses a supervised method to divide the data and;
\item
When planning how to move examples to better classes, it is best to reflect over 
differences between those classes.
\ei
\section{Future Work}
Future work in this area could explore numerous questions. For example, 
XTREE, as used here, sought improvements in a one goal (the class variable). Does XTREE work for multi-goal reasoning?

Also, the XTREE algorithm seems quite general to any data of table with rows containing
weighted classes (so we can distinguish ``bad'' rows from ``better'' ones). 
Does   XTREE works  on   domains (other than the defect/runtime data explored here)?

As an example of a domain that might benefit from XTREE, recent results raise doubts about
the value of changing code to remove ``bad smells''~\cite{Sjoberg13}. Can XTREE be used as a ``bad smell'' detector to select the subset of possible refactorings that have the most potential benefit?

As to scalability, XTREE is a post-processor to a decision tree algorithm. Hence, in theory, XTREE   works on domain where data miners can generate decision trees. Given the current state of the art in Big Data, can XTREE  be applied to  very large data sets?

We discussed above in \tion{p2p} the general  conclusions of Passos, J{\o}rgensen  et.al~\cite{passos11,jorgensen09};
i.e. software developers are reluctant to surrender their old biases
in the face of new data. 
Accordingly, it must be asked if  the {\em mental resistance} of developers
will prevent them applying XTREE's automatically generated recommendations of tools?
Note this this issue is not just a concern for XTREE, but also for any 
automatic tool proposing refactorings.

There are many more methods for generating plans and
no   one paper can survey them all. For example, this paper has not explored variations to the $\alpha,\beta$, and $\gamma$
parameters that controlled XTREE. Would we get better results if we varied those parameters?

>>>>

\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
\usepackage{times}
\pagenumbering{arabic}

\usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

% inner sep=10pt,
\tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
  fill=Gray!20,  drop shadow={fill=black, opacity=1}]
\newcommand\thmbox[1]{%
  \noindent\begin{tikzpicture}%
  \node [thmbox] (box){%
\begin{minipage}{.94\textwidth}%    
      \vspace{-3mm}#1\vspace{-3mm}%
    \end{minipage}%
  };%
  \end{tikzpicture}}

\let\theoremframecommand\thmbox
\newshadedtheorem{lesson}{Research answer}

\begin{document}

@@

\title{  Which ``Bad Smells'' can be Ignored?}
\numberofauthors{2} 
\author{  
\alignauthor
Rahul~Krishna, Tim Menzies  \\
       \affaddr{Computer Science, NC State, USA}\\
       {\{i.m.ralk,~tim.menzies\}@gmail.com}
\alignauthor
Lucas Layman \\
       \affaddr{Fraunhofer CESE, College Park, USA}\\ 
       {llayman@cese.fraunhofer.org}
\setlength{\columnsep}{7mm}}
\maketitle
\begin{abstract} 
The literature lists many   bad smells that may
be detrimental to a software system.
But which are relevant to the current project
and which can be ignored?
Developers, text books, and tools
disagree on which bad smells are important. 
Further, it is unclear at what threshold values smell-related metrics
should trigger code improvement or preventative maintenance. Most studies do not offer
{\em both} measurable metrics {\em and} a threshold for their proposed bad smells.

This paper proposes XTREE, a tool to prioritize  bad  smells.
Given an historical log of defects seen previously in the code, XTREE deprioritizes bad smells that have   no prior  association with defects.

We evaluate XTREE's recommendations for bad smell improvement against recommendations from previous work (Shatnawi, Alves, and Borges) using multiple data sets of code metrics and defect counts.  Code modules that are changed in response to XTREE's recommendations contain significantly fewer defects than recommendations in previous studies. 
  Further, XTREE endorses
  changes to far fewer code metrics, and that bad smell recommendations (learned from previous studies) are not universal to software projects.

Based on these results, we endorse using bad smells to  
guiding refactoring. However,
not all bad smells
are relevant to the current project. It is hence important
to  prioritize the importance of specific bad smells in the context of each project.

@@

\noindent
According to   Fowler~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk of introducing errors}'' (our italics).
\end{quote}
The literature is divided on the merits of bad smells.
Much research endorses them to guide
code improvement (e.g., refactoring or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
lists dozens of papers on smell detection and repair tools.

Other papers cast doubt on the value of bad smells
as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
As we show in this paper,  
 tools, text books, and developers disagree on what bad smells
are important enough to hunt down and eliminate. Our findings
are consistent with other research suggesting that universal bad
smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

% Debates on when and which code should be restructured are interesting, especially
% in the current context of  widely-used SE practices such as
% test-driven agile development~\cite{beck2003test,janzen05,williams2003test,george2003initial}.
% In that approach, developers are always asking themselves ``should I refactor this code''?
Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text has 6434 references. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

To address this problem, we propose the XTREE
tool to judge refactorings
proposed by developers.
  XTREE requires:
     \begin{itemize}
         \item An historical log of defects seen previously in the code;
         \item  Bad smells expressed in terms of the 
          metrics   in that log;
         \item Some proposed refactorings justified using those bad smells.
     \end{itemize}
Given that information,  XTREE can determine which
  proposed refactorings are be ignored
since they are not justifiable  
with respect to the history of the project.

@@

{\em PROBLEM \#1:} As discussed in the next section, programmer
   cognitive biases result in different
developers declaring that
bad smell X or Y is most important. 
 XTREE offers a way to assess the value of competing recommendations to address smell X vs. Y.

{\em PROBLEM \#2:} Not all bad smells can be fixed. 
Consider
a bad smell stemming from a long method,
yet that method must be passed as a single closure
to a third-party GUI toolkit.  This is one
example of a common problem-- when new code must
be combined with code from other developers,
sometimes the constraints imposed by the other code
lead unavoidably to bad smells. In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

To address this problem, XTREE {\em reasons optimistically} to find the set
$R_0$ of refactorings that \textit{might} be useful (see \tion{rq} on optimistic reasoning).
The space of \textit{actually usable} refactorings is 
the subset $R_1 \subseteq R_0$.
If a developer's proposed refactoring $R_2$ is
not in $R_0$, then it cannot be in the usable
set $R_1$.  We show experimentally that XTREE
often recommends small subsets of
code metrics as useful guides for refactoring. Thus, we
can rule out some proposed refactorings
since many of those proposals fall outside of the space
useful refactorings ($R_0$) suggested by XTREE.

{\em PROBLEM \#3:}  
Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
{\em both} a metric and a threshold for proposed bad smells. For example,  Darcy and Kemerer~\cite{darcy05}
discuss object-oriented (OO) design metrics that might defect bad smells (e.g. an excessive
depth of inheritance tree), but they do not define thresholds
for when the code starts to smell bad.  
Shatnami~\cite{Shatnawi10}
and  Alves et al.~\cite{Alves2010} are rare cases where both metrics and thresholds are defined (see \tion{methods}).
However, their approaches do not explore the interconnections between sets of code metrics. This is important if sets of
code metrics have to be changed at the same time.
For example, it is not possible to refactor a
long method it several smaller ones without increasing
the coupling metrics of a class. 
More generally, we say that bad smell thresholds should be
{\em conjunctions} of metric+threshold pairs that need to be changed {\em together}.
Shatnami~\cite{Shatnawi10}
and Alves et al. report {\em disjunctions} of multiple metrics+thresholds~\cite{Shatnawi10,Alves2010}
which could be separately and  inappropriately used
to guide refactoring.\footnote{From LL: I don't understand the conjunction/disjunction. Are you saying Metric1+Metric2 needs its own threshhold, or you need \{Metric1+Threshold1, Metric2+Threshold2\}. And what do Satnami and Alves do?}

@@

{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite since (refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
% waiting to observe 
% code refactorings is meant to
% preserve the behavior of the system (i.e. the same tests
% should pass before and after the refactoring). 
% Also, it many not be practical
%  to assessing refactorings by making the
% refactorings,  then seeing what happens to that code for the rest
% of the project. In a test-driven agile project, as
% SCRUM meetings change what stories are implemented next,
% the operational profile that lead to defects in the old
% code may not be repeated in future executions. 
To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of systems: 
\begin{enumerate}
    \item One system to propose changes;
\item A separate system to assess
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}.
A shortcoming of QMOOD
is that quality models learned from other projects
may perform poorly when applied to new projects~\cite{me12d}.

To solve this fourth problem, this study  eschews
older quality models like QMOOD, we use
Random Forests~\cite{Breiman2001} to learn defect predictors
from OO code metrics.
Note that, unlilke QMOOD, such measurements 
  are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.

The rest of this paper is structured as follows. XXX.
discusses the cognitive
biases that make developers disagree on the relevance of those bad smells to
their particular projects.  
 That discussion is our motivation for developing the XTREE  tool
that   carefully assesses the merit of old bad smells to new projects.  XTREE is presented in Section 3 and evalauted in the rest of the paper.

XTREE   is focused on Fowler's bad smells
as contributors to software defects. Some researchers 
 suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
about interactions within the code. In that view, 
the concept of refactoring can be useful
even if it does not address issues of defects. 
That said, using
defect predictors,
it is possible to operationalize XTREE
while it might be harder to otherwise operationalize the assessment of bad smells.
Hence, 
this paper assumes that {\em better} bad smells and
bettering at finding code changes that  {\em reducing} the chances
that the new code will contain defects.

@@

\subsection{Assessment Oracles}
\label{sect:eval}
Prior work~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} 
used the QMOOD hierarchical quality model ~\cite{Bansiya02} to assess the results of their refactorings
Since the QMOOD method is quite old (2002), we  used Random Forests~\cite{Breiman2001} to build
the assessment methods.

@@

The Scott-Knott  results are presented in the form of line diagrams like those shown on the right-hand-side of \fig{jur}
The black dot shows the median \eq{diff} values and the horizontal likes stretch 
from the 25th percentile to the 75th percentile (a region called the inter-quartile
range, or IQR).
As an example of how to read this table, consider the {\em Ant}
results. Those rows are  sorted on the median values of each method. Note that all the methods have \eq{diff} $\gt 0\%$; i.e. all these methods reduced the expected value of the performance score in that experiment while XTREE achieved the greatest reduction (of 56\% from the original value).
These results table has a  left-hand-side  {\bf Rank} column, computed using the
Scott-Knott test described above. In the {\em Ant}
results, XTREE is ranked the best, while CD is  ranked   worst.

% \begin{center}
% {\small
%   Example 
% \begin{tabular}{{l@{~~~}l@{~~~}r@{~~~~}r@{~~~}c@{}r}} 
% \arrayrulecolor{lightgray}
% \rowcolor{lightgray}\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\
% 1 &      XTREE &    62  &  6 & \quart{67.2}{7}{69.6}{115}  \\
% \hline 2   & Alves        &    40  & 20  & \quart{45}{10}{50}{10}\\
% \hline 3 &      CD &    24  &  18 & \quart{28}{14.4}{35.2}{115} \\
% \hline 4   & Shatnawi        &    15  & 10  & \quart{28}{5}{30}{10}\\\hline
% \end{tabular}}
% \end{center}

\input{tex/rq2.tex}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=\linewidth]{figs/changes01.png}
\caption{XTREE results.
While \fig{counts} are the {\em number} of times a code metric was changed,
\fig{changes} shows {\em how far} each code metric was changed. Each vertical bar
marks the 27,50,75th percentile change seen in 40 repeats. }
\label{figs:changes}
\end{figure*}

\subsubsection{RQ1: Effectiveness}

\fig{jur} shows the comparison results.  The Alves and Shatnami
entries show the  net effects of applying (seperately) all the disjuncts
proposed by those methods.

Two data sets are very responsive to defect reduction suggestions:
 Ant, and Ivy (both of which show best case improvements over 50\%).
 The  expected value of defects  
 is changed less in Jedit. This data sets' results
 surprisingly uniform; i.e.   all methods
 find the same ways to reduce the expected number of
defects.

@@

\begin{lesson}
In terms of the expected number of defects
  after refactoring,
XTREE is marginally better than Alves while CD and Shatnawi
are deprecated.
\end{lesson}

{\em In a comparison of outlier and cluster delta methods, which one proposes the fewest thresholds?}

\fig{counts} shows the frequency with which our different methods
require changes to code methods.
Note that XTREE proposes thresholds to
few code metrics than the other approaches.

\begin{lesson}
In  terms of how often   a bad
smell can be ignored, XTREE is best since it is  least verbose (i.e. least
likely to  overlap   a bad smell mentioned by a developer).
\end{lesson}

When combining   \fig{jur} with \fig{counts}, we   see that
even though XTREE proposes changes to far fewer code metrics, those few
code metrics are usually just as effective (or
more effective) than the multiple
thresholds
proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
{\em fewer} and better thresholds than the other approaches studied here.

\subsubsection{RQ3: Co-Change}

{\em Does XTREE understand what metrics get changed together?}
xxxx

@@

@@

\subsection{External Validity}
Based on the experimental results above,
as well as the discussion in \tion{prelim},
we believe that specific bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
have very limited external validity. 
The good news is that,
while specific models are not externally valid,
there may still be general methods like XTREE for finding the good local models.

One   limitation to certifying bad smells
is the terminology used to express the bad smell.
XTREE, Shatnawi, Alves et al. can  only comment
on refactorings expressed in the   terminology
as the data
  in the historical log of a project.
If developers want to justify their refactorings
via bad smells expressed in other terminology,
then the  analysis of this paper must   wait till 
data about those new
terms has been collected.

XTREE does not require a working defect predictor to generate
its bad smell thresholds. However, to {\em certify}
that those thresholds are satisfactory, some
second quality predictor must be applied. Historically,
SE researchers~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} have used the QMOOD hierarchical quality model~\cite{Bansiya02}.
Since such quality models may be very project specific~\cite{localvsglobal}, we prefer building local 
defect predictors using Random Forests. 
Our results show that when a defect log contains too few
non-defective examples then defector predictors
perform poorly (see the data sets in the last few lines of \fig{j})
as do their associated bad smell threshold generators
(recall the performance of Lucene and Poi in~\fig{jur}).

It should be noted that this is not a limitation of XTREE-- rather
it seems fundamental to the problem of certifying bad smells.
As evidence of this, recall that {\em all} the bad smell threshold generators of~\fig{jur}
had issues with the defect data sets with  many defects
(Lucene and Po).

@@

\subsection{ Learner Bias}
This study used two kinds of learners: (1) methods for suggesting
changes to code like Shatnawi, Alves et al., CD and XTREE;
(2) methods for assessing the changes proposed by these learners.
Prior studies implemented (2) using  the QMOOD hierarchical quality model
which is so old, that we suspect it may no longer be current. Hence,
we used Random Forests to build the assessment oracles that were specific
to the data sets used in this study. .We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.

Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
That said, we have taken care to document in this paper the decisions made by engineering
judgement that could effect our conclusions.

\subsection{  Sampling bias} 
Sampling bias threatens any data mining experiment; i.e., what matters
there may not be true here. For example, the data sets used here comes from two  Jureczko et al. and any biases in their selection procedures
threaten the validity of these results. 
That said,
the best we can do is define our methods and publicize our data and code so that other researchers can
try to repeat our results and, perhaps, point out a previously unknown bias
in our analysis. Hopefully, other researchers will emulate our methods in
order to repeat, refute, or improve our results.

\subsection{  Evaluation Bias}\label{sect:coc}

The main evaluation bias in this study was the use of
optimistic reasoning when generating the changed code modules.
We assumed in \tion{rq}
that any code module can be changed in order
to stop triggering a bad smell detector. This is not necessarily
true, as noted in {\em PROBLEM \#2} in this paper's introduction.
To mitigate this issue, we do not propose using XTREE as a bad
smell generator, but as a critique agent for bad smells
proposed by some other oracle (e.g. a human developer).
We showed about that XTREE's recommendations are not verbose
so it will not often overlap with some random bad smell proposed
by a developer.

@@

\section{Conclusions}
When can bad smells be ignored? Our answer is as follows.
When those
bad smells are not supported by the historical log of data from
the current project.

When that data is not available (e.g. early
in the project) then developers could use the general list of
bad smells shown in \fig{smells}. However, 
our results
show that  bad smell detectors are most
effective when they are based
on a small handful of code metrics (as done by XTREE).
Hence, using all the bad smells of \fig{smells} may not be optimal.

XTREE improves on prior methods for generating bad smells:
\begin{itemize}
    \item As described in \tion{prelim}, bad smells generated by humans may not be apply to the current project. On the other hand, XTREE can learn specific thresholds for the current project.
    \item As described in in \tion{}, XTREE generates conjunctions
    \item Prior methods used an old quality predictor (QMOOD) which we replace with defect predictors learned from the current project.
\end{itemize}
